Radio Sources in the Central Filament of the Serpens South Protocluster

### 2014-12-17 Paper/paper.tex
new file:   IRAM_sources.reg 	modified:   Make_Figs.py 	modified:   Paper/figures/SerpSouth_zoom_color_contour-eps-converted-to.pdf 	modified:   Paper/figures/SerpSouth_zoom_contour-eps-converted-to.pdf 	modified:   Paper/paper.pdf 	modified:   Paper/paper.tex 	modified:   Paper/references.bib 	new file:   Radio_Correlations.py 	modified:   SERPS_SED.py 	modified:   git_add.sh

%% Begin Document
\begin{document}
%\submitted{Submitted: \today}
\title{Radio Sources in the Serpens South Protocluster}
\author{Authors}

@@

	Serpens South is a young stellar cluster that is a part of the broader Aquila Rift extinction feature. It lies south of the Serpens Main cloud, and is just West of the bright W40 HII region. Discovered in 2008 by \citet{Gutermuth08} as a part of the Spitzer Space Telescope's Gould Belt Legacy survey, Serpens South has been found to harbor an unusually high ratio of Class I to Class II protostars, suggesting it is in a very early phase of cluster formation. Since its discovery, it has become the center of a wide range of scholarship. This has consisted of near, mid and far infrared mappings with Spitzer and Herschel tracing heated dust around protostars \citep{Gutermuth08, Bontemps10}, millimeter mappings with MAMBO on the IRAM 30-meter tracing cold dust \citep{Maury11}, near infrared polarimetry revealing the importance of global magnetic fields in the cluster's formation history \citep{Sugitani11}, molecular outflows studies \citep{Nakamura11, Teixeira12}, and a wealth of spectral line surveys probing filamentary infall \citep{Kirk13, Friesen13, Tanaka13, FernandezLopez14,Nakamura14a}. X-ray studies of Serpens South have yet to be published. Presently only one radio study of Serpens South has been conducted, which used the VLA in its A configuration in 2011 (Ortiz-Leon et al. in prep). Beyond this study, further radio studies of Serpens South will be important in understanding the star formation process across the electromagnetic spectrum.

	The VLA has been a proven tool in searching for and detecting radio emission around protostars since the early 1990s \citep[e.g.,][]{Curiel89, Anglada98, Reipurth99, Beltran01, Eiroa05, Shirley07, Rodriguez10}. Early radio studies of protostars found an excess of radio emission in comparison to the Lyman-Alpha continuum drop off expected from a normal ZAMS star. Theory and observations have best explained protostellar radio emission as having two components: thermal and non-thermal. Thermal radio emission is generally assumed to be free-free emission created from an HII region. High mass protostars have a high enough internal luminosity to support a compact or ultra-compact HII region, however, low mass protostars do not. HII regions surrounding low-mass protostars are created from thermal jets that shock the material surrounding the protostar. Non-thermal emission around low and high mass protostars is still not clearly understood; it is thought to come from gyrosynchrotron emission or possibly from jets that produce synchrotron emission in their tails.

%	  Centimeter continuum emission is largely associated with free-free emission created from ionized regions within the dense envelope surrounding the star \citep{Anglada95}. High-mass protostars are strong enough to create this region from stellar winds, while low-mass protostars likely create these regions from compact, collimated thermal outflows, however photoionization and stellar winds from low-mass protostars may also help sustain HII regions around the protostar \citep{Scaife12}. Because radio observations probe deep into the stellar envelope, centimeter observations of this nature have been a proven tool in the detection of outflow sources \citep{Rodriguez97} and in the exploration of the physical dynamics of the youngest protostellar objects \citep{Anglada98,Shirley07}. In this respect, centimeter observations of protostars are a crucial asset in our understanding of regions of active star formation.

@@

The distances to Serpens South, W40 and the Serpens Main cloud are not agreed upon in the literature. When Serpens South was discovered in 2008, a distance of 260 pc $\pm$ 37 pc was adopted based on evidence that its LSR velocities matched LSR velocities of the Serpens Main cloud, which was then thought to be a part of the larger Aquila Rift extinction feature whose distance was estimated at 260 pc by \citet{Straizys03}. However, VLBA parallax measurements done in 2010 have established the distance to the Serpens Main cloud as 429 $\pm$ 2 pc \citep{Dzib11}, meaning that Serpens Main is distinct from the the Aquila Rift if the latter is to have a distance of 260 pc.

\citet{Gutermuth08} also argued that Serpens South lies in front of W40, claiming that it is seen in absorption against emission from W40. Therefore, we know Serpens Main is at 429 pc, and we know that Serpens South lies in front of W40. What we don't know are the absolute distances to both W40 or Serpens South. If we are to follow the initial LSR velocity analysis by \citet{Gutermuth08}, we would equate Serpens South to Serpens Main and say Serpens South lies at approximately 429 pc, while W40 lies further away. Indeed, recent radio and x-ray studies adopt a distance of 600 pc to W40, although they admit the distance is poorly constrained \citep{Kuhn10, Rodriguez10}. Here, we adopt a distance of 429 pc for Serpens South, although we comment on how a 260 pc distance estimate would change our analysis.

@@

%%%%%%%%%%%% Begin Table %%%%%%%%%%%%%%%%
\capstartfalse
\begin{deluxetable}{cccc}
\tabletypesize{\footnotesize}
\tablecaption{EVLA Image Properties}
\tablehead{
	\multicolumn{1}{c}{Wavelength}			&
	\multicolumn{1}{c}{Beam Size$^{a}$}		&
	\multicolumn{1}{c}{Position Angle}			&
	\multicolumn{1}{c}{Image RMS}					\\
	\colhead{(cm)}							&
	\colhead{(arcsec x arcsec)}					&
	\colhead{(degrees)}							&
	\colhead{($\mu$Jy beam$^{-1}$)}			}
\startdata
6.31	&	4.8 x 3.9	&	13.4	&	11.1	\\[1ex]
4.14	&	3.2 x 2.5	&	12.7	&	8.5
\enddata
\tablenotetext{a}{Images deconvolved with robust (Briggs) weighting, \emph{robust}=0.5 \citep{Briggs95}.}
\label{tab:image_pars}
\end{deluxetable}
\capstarttrue
%%%%%%%%%%% End Table %%%%%%%%%%%%%%%

@@

%%%%%%%%%%%% Begin Table %%%%%%%%%%%%%%%%
\capstartfalse
\begin{deluxetable*}{lcccccccc}
\label{tab:flux_table}
\tabletypesize{\footnotesize}
\tablecaption{Radio Properties of VLA Sources}
\tablehead{
	\multicolumn{1}{c}{Source}								&
	\multicolumn{1}{c}{RA$^{a}$}								&
	\multicolumn{1}{c}{Decl.$^{a}$}							&
	\multicolumn{1}{c}{$S^{\text{int}}_{6.3 \text{cm}}\ ^{b}$}			&
	\multicolumn{1}{c}{$S^{\text{peak}}_{6.3 \text{cm}}$}				&
	\multicolumn{1}{c}{$S^{\text{int}}_{4.1 \text{cm}}$}				&
	\multicolumn{1}{c}{$S^{\text{peak}}_{4.1 \text{cm}}$}				&
	\multicolumn{1}{c}{$\alpha^{\text{int}}_{\text{radio}}$}				&
	\multicolumn{1}{c}{$\alpha^{\text{peak}}_{\text{radio}}$}				\\ [.25ex]		
%	\multicolumn{1}{c}{L$_{\text{infrared}}$}				&
%	\multicolumn{1}{c}{L$_{\text{bol}}$}					&
%	\multicolumn{1}{c}{Match?}						&
%	\multicolumn{1}{c}{Evolutionary}					\\ [.25ex]
	\colhead{}										&
	\colhead{(J2000)}								&
	\colhead{(J2000)}								&
	\colhead{($\mu$Jy)}								&
	\colhead{($\mu$Jy beam$^{-1}$)}					&
	\colhead{($\mu$Jy)}								&
	\colhead{($\mu$Jy beam$^{-1}$)}					&
	\colhead{}										&
	\colhead{}										
%	\colhead{(L$_{\text{sun}}$)}						&
%	\colhead{(L$_{\text{sun}}$)}						&
%	\colhead{(MM/Hersc/Spitz)}						&
%	\colhead{Stage}								
	}
\startdata

VLA\_1	&	18:30:09.68	&	-02:00:32.8	&	844 $\pm$ 8	&	794	&	749 $\pm$ 6	&	718	&	0.28 $\pm$ 0.01	&	0.24 $\pm$ 0.02\\[1ex]

VLA\_2	&	18:30:04.79	&	-02:00:34.1	&	87 $\pm$ 7	&	72	&	177 $\pm$ 7	&	138	&	-1.67 $\pm$ 0.09	&	-1.55 $\pm$ 0.14\\[1ex]

VLA\_3	&	18:30:02.55	&	-02:00:48.5	&	116 $\pm$ 10	&	87	&	140 $\pm$ 2	&	99	&	-0.46 $\pm$ 0.1	&	-0.3 $\pm$ 0.15\\[1ex]

VLA\_4	&	18:30:01.53	&	-02:00:51.6	&	946 $\pm$ 28	&	515	&	1663 $\pm$ 32	&	1178	&	-1.33 $\pm$ 0.04	&	-1.96 $\pm$ 0.02\\[1ex]

VLA\_5	&	18:30:14.79	&	-02:01:27.3	&	167 $\pm$ 10	&	173	&	106 $\pm$ 5	&	95	&	1.07 $\pm$ 0.08	&	1.41 $\pm$ 0.13\\[1ex]

VLA\_6	&	18:30:06.62	&	-02:01:28.9	&	33 $\pm$ 4	&	56	&	79 $\pm$ 7	&	61	&	-2.04 $\pm$ 0.16	&	-0.22 $\pm$ 0.23\\[1ex]

VLA\_7	&	18:30:05.81	&	-02:01:44.9	&	84 $\pm$ 7	&	63	&	48 $\pm$ 4	&	40	&	1.29 $\pm$ 0.13	&	1.08 $\pm$ 0.31\\[1ex]

VLA\_8	&	18:30:06.89	&	-02:02:11.5	&	50 $\pm$ 6	&	50	&	39 $\pm$ 3	&	46	&	0.55 $\pm$ 0.15	&	0.18 $\pm$ 0.29\\[1ex]

VLA\_9	&	18:30:02.80	&	-02:02:25.3	&	60 $\pm$ 1	&	44	&	66 $\pm$ 1	&	50	&	-0.22 $\pm$ 0.03	&	-0.31 $\pm$ 0.29\\[1ex]

VLA\_10	&	18:30:02.95	&	-02:02:32.2	&	260 $\pm$ 17	&	73	&	287 $\pm$ 6	&	119	&	-0.23 $\pm$ 0.07	&	-1.15 $\pm$ 0.15\\[1ex]

VLA\_11	&	18:30:03.36	&	-02:02:45.8	&	73 $\pm$ 4	&	58	&	38 $\pm$ 2	&	36	&	1.5 $\pm$ 0.09	&	1.14 $\pm$ 0.34\\[1ex]

VLA\_12	&	18:30:04.11	&	-02:03:02.1	&	79 $\pm$ 2	&	58	&	30 $\pm$ 2	&	24	&	2.31 $\pm$ 0.09	&	2.06 $\pm$ 0.48\\[1ex]

VLA\_13	&	18:30:03.54	&	-02:03:08.4	&	231 $\pm$ 3	&	227	&	186 $\pm$ 1	&	178	&	0.51 $\pm$ 0.02	&	0.58 $\pm$ 0.07\\[1ex]

VLA\_14	&	18:30:03.84	&	-02:03:12.2	&	83 $\pm$ 2	&	61	&	31 $\pm$ 0	&	37	&	2.29 $\pm$ 0.04	&	1.19 $\pm$ 0.33\\[1ex]

VLA\_15	&	18:30:04.60	&	-02:03:14.1	&	49 $\pm$ 4	&	51	&	68 $\pm$ 1	&	52	&	-0.74 $\pm$ 0.09	&	-0.08 $\pm$ 0.27\\[1ex]

VLA\_16	&	18:30:03.25	&	-02:03:26.6	&	55 $\pm$ 1	&	65	&	63 $\pm$ 2	&	58	&	-0.28 $\pm$ 0.04	&	0.27 $\pm$ 0.23\\[1ex]

VLA\_17	&	18:30:01.32	&	-02:03:42.9	&	161 $\pm$ 4	&	167	&	146 $\pm$ 3	&	135	&	0.22 $\pm$ 0.04	&	0.5 $\pm$ 0.1\\[1ex]

VLA\_18	&	18:30:09.40	&	-02:04:08.8	&	167 $\pm$ 10	&	134	&	170 $\pm$ 3	&	182	&	-0.04 $\pm$ 0.07	&	-0.71 $\pm$ 0.09

\enddata
\tablenotetext{a}{Centers of 2D gaussian fits for sources in 4.1 cm map, quoted in J2000 coordinates.}
\tablenotetext{b}{Flux values from images deconvolved with Briggs weighting, \emph{robust}=0.5 \citep{Briggs95}.}
\tablenotetext{c}{Spectral index of integrated flux from 6.3 to 4.1 cm, see \autoref{sec:results} for details on calculation.}
\tablenotetext{d}{Spectral index of peak flux from 6.3 to 4.1 cm.}
\tablenotetext{e}{}

@@

In choosing our sources, we restrict ourself to a circular region centered on our phase center and extending out to 50\% of the primary beam strength. We choose our sources based on their strength in our 4.1 and 6.3 cm maps, their possible spatial alignment with infrared sources, and by referencing a source extracted sample using Sextractor \citep{Bertin96}. We were left with a total of 18 radio sources. We then ran source extractions on these spatial positions over the JHK bands of 2MASS, the four IRAC bands of Spitzer, the 24 $\mu$m MIPS band on Spitzer, and the 70 $\mu$m PACS band on Herschel. We used a 2 arcsecond maximum matching tolerance for these extractions. Apertures and adopted corrections are consistent with the HOPS survey.

@@

\begin{figure*}
\epsscale{1.15}
\plottwo{figures/SerpSouth_zoom_contour.eps}{figures/SerpSouth_zoom_color_contour.eps}
\caption{{\bfseries Left}: Radio continuum of central filament at 6.3 cm, focused in on red box from \autoref{fig:serpsouth_fov_contour}. Blue and red crosses correspond to Class I and II protostars identified by Spitzer \citep{Gutermuth08}. Green crosses correspond to 1.2 mm dust peaks identified by IRAM \citep{Maury11}. {\bfseries Right}: Identical image as figure on the left, but the background color is PACS 70 $\mu$m image.}
\end{figure*}

Eight of our radio sources have at least one infrared source match from 1.25 $\mu$m to 70 $\mu$m, four of which spatially match Spitzer identified Class I/II protostars within 1 arcsecond. A total of ten out of our 18 sources have signs that indicate they are protostellar in nature. One of our radio sources matches a 1.2 mm source within 1 arcsecond identified by \citep{Maury11}, which they state as starless. Here, we confirm compact radio emission with a rising spectral index indicative of mixed optically thin and thick free-free emission, which suggests the presence of a compact core.

We can calculate the number of random background sources we would expect to find in our images. We use the formulation found in \citet{Shirley07}, who draw from radio studies done by \citet{Fomalont91}. The density of random background radio sources above a flux limit of $S\ \mu$Jy at 6 cm is given by $N(>S) = 0.42\cdot(S/30\ \mu \text{Jy})^{-1.18}$ arcmin$^{-2}$. Therefore, the total number of sources with flux $S$ greater than 50 $\mu$Jy at 6 cm is 0.229 arcmin$^{-2}$. This leads to a 0.4\% chance that a background source falls inside any one synthesized beam centered on a compact star, and gives us on average $\sim$9 background sources above 50 $\mu$Jy within our 3.5' x 3.5' region of interest. This agrees with our analysis, as we find roughly 8 sources that are likely background sources.

@@

\subsection{Radio Source Properties}
\label{sec:radio source properties}

@@

\sourcenote{VLA 1 - 5}
VLA 1 is relatively isolated from the cluster, has very strong radio emission and has no known protostellar matches in the infrared. These alone would suggest an extragalactic classification, however, it has a slightly rising radio spectral index of 0.28 indicative of optically thin free-free emission. While galaxies are capable of producing  free-free emission from large HII regions, non-thermal synchrotron emission with a steep negative spectral index generally dominates a galaxies' radio emission output. However, because VLA 1 does not spatially match any near or far infrared emission structures, we conclude it is extragalactic in nature.

Sources 2 through 4 seem to be extragalactic. They have no infrared or far-infrared matches and have steep negative radio spectral indices that suggests their emission is non-thermal synchrotron.

VLA 5 is isolated from the cluster and has no infrared or far-infrared matches, but has a strongly rising radio spectral index of 1.41 suggesting that it comes from optically thick free-free emission. Similar to VLA 1, we conclude that it is extragalactic.

@@

The Serpens South embedded cluster occupies a region in projected proximity to the larger Aquila Rift complex, the W40 HII region and the Serpens Main molecular cloud. The Aquila Rift, as previously noted, is a local complex of dark molecular clouds extending several degrees, encompassing the Serpens Main molecular cloud, Serpens South and the W40 HII region (see Figure 1), which are the three main regions of star formation in the direction of the Aquila Rift \citep{Eiroa08}.

@@

\appendix
{\large These are my edit notes for the paper.} \\[.25in]

>>>>

%% Begin Document
\begin{document}
%\submitted{Submitted: \today}
\title{Radio Sources in the Central Filament of the Serpens South Protocluster}
\author{Authors}

@@

	Serpens South is a young stellar cluster that is a part of the broader Aquila Rift extinction feature. It lies south of the Serpens Main cloud and is just West of the bright W40 HII region. Discovered in 2008 by \citet{Gutermuth08} as a part of the Spitzer Space Telescope's Gould Belt Legacy survey, Serpens South has been found to harbor an unusually high ratio of Class I to Class II protostars suggesting it is in a very early phase of cluster formation. Since its discovery, it has become the center of a wide range of scholarship. This has consisted of near, mid and far infrared mappings with Spitzer and Herschel tracing heated dust around protostars \citep{Gutermuth08, Bontemps10}, millimeter mappings with MAMBO on the IRAM 30-meter tracing cold dust \citep{Maury11}, near infrared polarimetry revealing the importance of global magnetic fields in the cluster's formation history \citep{Sugitani11}, molecular outflows studies \citep{Nakamura11, Teixeira12}, and a wealth of spectral line surveys probing filamentary infall \citep{Kirk13, Friesen13, Tanaka13, FernandezLopez14,Nakamura14a}. X-ray studies of Serpens South have yet to be published. Presently only one radio study of Serpens South has been conducted, which used the VLA in its A configuration in 2011 (Ortiz-Leon et al. in prep).

	Because of its isolated formation, Serpens South presents a unique opportunity to study the environmental influences on protostars in a young stellar cluster. A multi-wavelength approach will be key to fully understanding to non-normative behaviors of protostars in a high-density environment such as Serpens South.

	The VLA has been a proven tool in searching for and detecting radio emission around protostars since the early 1990s \citep[e.g.,][]{Curiel89, Anglada98, Reipurth99, Beltran01, Eiroa05, Shirley07, Rodriguez10}. Early radio studies of protostars found an excess of radio emission in comparison to the Lyman-Alpha continuum drop off expected from a normal ZAMS star. Theory and observations have best explained protostellar radio emission as having two components, thermal and non-thermal. Thermal radio emission is generally assumed to be free-free emission created from an HII region. High mass protostars have a high enough internal luminosity to support a compact or ultra-compact HII region, however, low mass protostars do not. HII regions surrounding low-mass protostars are created from thermal jets that shock the material surrounding the protostar. Non-thermal emission around low and high mass protostars is still not clearly understood; it is thought to come from gyrosynchrotron emission or possibly from jets that produce synchrotron emission in their tails.

	Towards the two goals of 1) locating new embedded protostars in the Serpens South protocluster and 2) better understanding the mechanisms of protostellar radio emission on a global scale, we carried out EVLA observations of Serpens South's central filament at 4.1 and 6.3 centimeters. In $\S 2$ we present our observations. In $\S 3$ we present our results. In $\S 4$ we discuss the implications of our study and in $\S 5$ we summarize our results.

@@

The distances to Serpens South, W40 and the Serpens Main cloud are not agreed upon in the literature. When Serpens South was discovered in 2008, a distance of 260 pc $\pm$ 37 pc was adopted based on evidence that its LSR velocities matched LSR velocities of the Serpens Main cloud, which was then thought to be a part of the larger Aquila Rift extinction feature estimated to lie at 260 pc \citep{Straizys03}. However, VLBA parallax measurements conducted in 2010 have established the distance to the Serpens Main cloud as 429 $\pm$ 2 pc \citep{Dzib11}, meaning that Serpens Main is distinct from the the Aquila Rift if Aquila is to have a distance of 260 pc.

\citet{Gutermuth08} also argued that Serpens South lies in front of W40, claiming that it is seen in absorption against emission from W40. If we are to follow the initial LSR velocity analysis by \citet{Gutermuth08}, we would equate Serpens South to Serpens Main and say Serpens South lies at approximately 429 pc, while W40 lies further away. Indeed, recent radio and x-ray studies adopt a distance of 600 pc to W40, although they admit the distance is poorly constrained \citep{Kuhn10, Rodriguez10}. Here, we adopt a distance of 429 pc for Serpens South, although we comment on how a 260 pc distance estimate would change our analysis.

@@

%%%%%%%%%%%% Begin Table %%%%%%%%%%%%%%%%
\capstartfalse
\begin{deluxetable}{cccc}
\tabletypesize{\footnotesize}
\tablecaption{EVLA Image Properties}
\tablehead{
	\multicolumn{1}{c}{Wavelength}			&
	\multicolumn{1}{c}{Beam Size$^{a}$}		&
	\multicolumn{1}{c}{Position Angle}			&
	\multicolumn{1}{c}{Image RMS}					\\
	\colhead{(cm)}							&
	\colhead{(arcsec x arcsec)}					&
	\colhead{(degrees)}							&
	\colhead{($\mu$Jy beam$^{-1}$)}			}
\startdata
6.31	&	4.8 x 3.9	&	13.4	&	11.1	\\[1ex]
4.14	&	3.2 x 2.5	&	12.7	&	8.5
\enddata
\tablenotetext{a}{Deconvolved with robust weighting, \emph{robust}=0.5 \citep{Briggs95}.}
\label{tab:image_pars}
\end{deluxetable}
\capstarttrue
%%%%%%%%%%% End Table %%%%%%%%%%%%%%%

@@

%%%%%%%%%%%% Begin Table %%%%%%%%%%%%%%%%
\capstartfalse
\begin{deluxetable*}{lccccccccc}
\label{tab:flux_table}
\tabletypesize{\footnotesize}
\tablecaption{Radio Properties of VLA Sources}
\tablehead{
	\multicolumn{1}{c}{Source}								&
	\multicolumn{1}{c}{RA$^{a}$}								&
	\multicolumn{1}{c}{Decl.$^{a}$}							&
	\multicolumn{1}{c}{$S^{\text{int}}_{6.3 \text{cm}}\ ^{b}$}			&
	\multicolumn{1}{c}{$S^{\text{peak}}_{6.3 \text{cm}}$}				&
	\multicolumn{1}{c}{$S^{\text{int}}_{4.1 \text{cm}}$}				&
	\multicolumn{1}{c}{$S^{\text{peak}}_{4.1 \text{cm}}$}				&
	\multicolumn{1}{c}{$\alpha^{\text{int}}_{\text{radio}}$}			&
	\multicolumn{1}{c}{$\alpha^{\text{peak}}_{\text{radio}}$}			&	
	\multicolumn{1}{c}{Class$^{e}$}							\\ [.25ex]	
%	\multicolumn{1}{c}{L$_{\text{infrared}}$}				&
%	\multicolumn{1}{c}{L$_{\text{bol}}$}					&
%	\multicolumn{1}{c}{Match?}						&
%	\multicolumn{1}{c}{Evolutionary}					\\ [.25ex]
	\colhead{}										&
	\colhead{(J2000)}								&
	\colhead{(J2000)}								&
	\colhead{($\mu$Jy)}								&
	\colhead{($\mu$Jy beam$^{-1}$)}					&
	\colhead{($\mu$Jy)}								&
	\colhead{($\mu$Jy beam$^{-1}$)}					&
	\colhead{}										&
	\colhead{}										&
	\colhead{}	
%	\colhead{(L$_{\text{sun}}$)}						&
%	\colhead{(L$_{\text{sun}}$)}						&
%	\colhead{(MM/Hersc/Spitz)}						&
%	\colhead{Stage}								
	}
\startdata

VLA\_1	&	18 30 09.68	&	-02 00 32.8	&	749 $\pm$ 6	&	718	&	844 $\pm$ 8	&	794	&	0.28 $\pm$ 0.01	&	0.24 $\pm$ 0.02	&	Extragal.?\\[1ex]

VLA\_2	&	18 30 04.79	&	-02 00 34.1	&	177 $\pm$ 7	&	138	&	87 $\pm$ 7	&	72	&	-1.67 $\pm$ 0.09	&	-1.55 $\pm$ 0.14	&	Extragal.\\[1ex]

VLA\_3	&	18 30 02.55	&	-02 00 48.5	&	140 $\pm$ 2	&	99	&	116 $\pm$ 10	&	87	&	-0.46 $\pm$ 0.1	&	-0.3 $\pm$ 0.15	&	Extragal.\\[1ex]

VLA\_4	&	18 30 01.53	&	-02 00 51.6	&	1663 $\pm$ 32	&	1178	&	946 $\pm$ 28	&	515	&	-1.33 $\pm$ 0.04	&	-1.96 $\pm$ 0.02	&	Extragal.\\[1ex]

VLA\_5	&	18 30 14.79	&	-02 01 27.3	&	106 $\pm$ 5	&	95	&	167 $\pm$ 10	&	173	&	1.07 $\pm$ 0.08	&	1.41 $\pm$ 0.13	&	Extragal.?\\[1ex]

VLA\_6	&	18 30 06.62	&	-02 01 28.9	&	79 $\pm$ 7	&	61	&	33 $\pm$ 4	&	56	&	-2.04 $\pm$ 0.16	&	-0.22 $\pm$ 0.23	&	Extragal.\\[1ex]

VLA\_7	&	18 30 05.81	&	-02 01 44.9	&	48 $\pm$ 4	&	40	&	84 $\pm$ 7	&	63	&	1.29 $\pm$ 0.13	&	1.08 $\pm$ 0.31	&	Class I\\[1ex]

VLA\_8	&	18 30 06.89	&	-02 02 11.5	&	39 $\pm$ 3	&	46	&	50 $\pm$ 6	&	50	&	0.55 $\pm$ 0.15	&	0.18 $\pm$ 0.29	&	Extragal.?\\[1ex]

VLA\_9	&	18 30 02.80	&	-02 02 25.3	&	66 $\pm$ 1	&	50	&	60 $\pm$ 1	&	44	&	-0.22 $\pm$ 0.03	&	-0.31 $\pm$ 0.29	&	Class 0?\\[1ex]

VLA\_10	&	18 30 02.95	&	-02 02 32.2	&	287 $\pm$ 6	&	119	&	260 $\pm$ 17	&	73	&	-0.23 $\pm$ 0.07	&	-1.15 $\pm$ 0.15	&	Unknown\\[1ex]

VLA\_11	&	18 30 03.36	&	-02 02 45.8	&	38 $\pm$ 2	&	36	&	73 $\pm$ 4	&	58	&	1.5 $\pm$ 0.09	&	1.14 $\pm$ 0.34	&	Class 0\\[1ex]

VLA\_12	&	18 30 04.11	&	-02 03 02.1	&	30 $\pm$ 2	&	24	&	79 $\pm$ 2	&	58	&	2.31 $\pm$ 0.09	&	2.06 $\pm$ 0.48	&	Class 0$^{*}$\\[1ex]

VLA\_13	&	18 30 03.54	&	-02 03 08.4	&	186 $\pm$ 1	&	178	&	231 $\pm$ 3	&	227	&	0.51 $\pm$ 0.02	&	0.58 $\pm$ 0.07	&	Class 0$^{*}$\\[1ex]

VLA\_14	&	18 30 03.84	&	-02 03 12.2	&	31 $\pm$ 0	&	37	&	83 $\pm$ 2	&	61	&	2.29 $\pm$ 0.04	&	1.19 $\pm$ 0.33	&	Class 0$^{*}$\\[1ex]

VLA\_15	&	18 30 04.60	&	-02 03 14.1	&	68 $\pm$ 1	&	52	&	49 $\pm$ 4	&	51	&	-0.74 $\pm$ 0.09	&	-0.08 $\pm$ 0.27	&	Extragal.\\[1ex]

VLA\_16	&	18 30 03.25	&	-02 03 26.6	&	63 $\pm$ 2	&	58	&	55 $\pm$ 1	&	65	&	-0.28 $\pm$ 0.04	&	0.27 $\pm$ 0.23	&	Class II\\[1ex]

VLA\_17	&	18 30 01.32	&	-02 03 42.9	&	146 $\pm$ 3	&	135	&	161 $\pm$ 4	&	167	&	0.22 $\pm$ 0.04	&	0.5 $\pm$ 0.1	&	Class I\\[1ex]

VLA\_18	&	18 30 09.40	&	-02 04 08.8	&	170 $\pm$ 3	&	182	&	167 $\pm$ 10	&	134	&	-0.04 $\pm$ 0.07	&	-0.71 $\pm$ 0.09	&	Extragal.?

\enddata
\tablenotetext{a}{Centers of 2D gaussian fits for sources in 4.1 cm map, quoted in J2000 coordinates.}
\tablenotetext{b}{Flux values from images deconvolved with Briggs weighting, \emph{robust}=0.5 \citep{Briggs95}.}
\tablenotetext{c}{Spectral index of integrated flux from 6.3 to 4.1 cm, see \autoref{sec:results} for details on calculation.}
\tablenotetext{d}{Spectral index of peak flux from 6.3 to 4.1 cm.}
\tablenotetext{e}{Classification of source. Unless otherwise noted, Class 0 classifications come from Herschel \citep{Bontemps10} and Class I \& II  from Spitzer \citep{Gutermuth08}. (?) denotes uncertaintity. ($^{*}$) denotes classified by this work.}

@@

In choosing our sources, we restricted ourself to a circular region centered on our phase center and extending out to 50\% of the primary beam strength. We chose our sources based on their strength in our 4.1 and 6.3 cm maps, their possible spatial alignment with infrared sources, and by referencing a source extracted sample using Sextractor \citep{Bertin96}. We took only sources that had at least a $4\sigma$ strength in the 4.1 cm image, and were left with a total of 18 radio sources. We note that we found $\sim$6 sources at the $2\sigma$ level that aligned within 2 arcsecond of an infrared association, however, we do not consider them strong detections and do not include them in our final source list. As stated in \autoref{sec:observations}, further observations with longer integration will likely be able to confidently detect these protostellar radio sources.

@@

\begin{figure*}
\label{fig:zoom}
\epsscale{1.15}

\plottwo{figures/SerpSouth_zoom_contour.eps}{figures/SerpSouth_zoom_color_contour.eps}
\caption{{\bfseries Left}: Radio continuum at 6.3 cm focused in on red box from \autoref{fig:serpsouth_fov_contour}. Blue and red crosses correspond to Spitzer identified Class I and II protostars. Green crosses correspond to 1.2 mm dust peaks identified by IRAM. {\bfseries Right}: Identical contours on the left but with a background PACS 70 $\mu$m image. The radio contour beam size is shown to the lower-left.}
\end{figure*}

We ran source extractions on the spatial positions of our final source list over the JHK bands of 2MASS, the four IRAC bands of Spitzer, the 24 $\mu$m MIPS band on Spitzer, and the 70 $\mu$m PACS band on Herschel. We used a 2 arcsecond maximum matching tolerance for these extractions. Apertures and adopted corrections were consistent with the HOPS survey.

Eight of our radio sources have at least one infrared source match from 1.25 $\mu$m to 70 $\mu$m, four of which spatially match Spitzer identified Class I/II protostars within 1 arcsecond. A total of ten out of our 18 sources have signs that indicate they are protostellar in nature. One of our radio sources, VLA 12, matches a 1.2 mm source within 1 arcsecond identified by \citep{Maury11}, which they quote as starless.

We can calculate the number of random background sources we would expect to find in our images. We use the formulation found in \citet{Shirley07}, who draw from radio studies done by \citet{Fomalont91}. The density of random background radio sources above a flux limit of $S\ \mu$Jy at 6 cm is given by $N(>S) = 0.42\cdot(S/30\ \mu \text{Jy})^{-1.18}$ arcmin$^{-2}$. Therefore, the total number of sources with flux $S$ greater than 50 $\mu$Jy at 6 cm is 0.229 arcmin$^{-2}$. This leads to a 0.4\% chance that a background source falls inside any one synthesized beam centered on a compact radio source, and gives us on average $\sim$9 background sources above 50 $\mu$Jy within our 3.5' x 3.5' region of interest. This agrees with our analysis, as we find roughly 8 sources that are likely background sources.

@@

\subsection{Radio Source Classifications}
\label{sec:radio source classifications}

@@

\sourcenote{Extragalactic Sources}
VLA 2, 3, 4, 6, and 15 are very likely extragalactic in nature. They have no visible associations from 1$\mu$m to 70$\mu$m and have negative radio spectral indices indicative of non-thermal synchrotron emission.

\sourcenote{Unclear Sources}
While VLA 1 and 5 have no infrared, far-infrared or millimeter associations and are isolated from the filament, they have a flat and rising radio spectral indices suggesting optically thin and thick free-free emission respectively. Although galaxies can produce free-free emission from large HII clouds, the dominant component of a galaxy's radio emission output comes from non-thermal synchrotron emission with a declining spectrum. Nonetheless, we tentatively classify these sources as extragalactic due to their lack of associations.

VLA 18 is spatially distinct from the filament but has a flat radio spectral index and actually has three very weak infrared associations at 3.6, 4.5 and 5.8 $\mu$m. However, we speculate that these associations are coincidental and tentatively classify VLA 18 as extragalactic.

\begin{figure}
\label{fig:serpsouth_vla10_contour}
\centering
\includegraphics[keepaspectratio=True,scale=.3]{figures/SerpSouth_VLA10_contour.eps}
\caption{\small{Zoom in of the elongated VLA 10 source. Blue solid and red dashed contours correspond to 4.1 and 6.3 cm images respectively. The lower-left beam is the 4.1 cm beam size. Blue crosses represent Spitzer identified Class I sources.
}}
\end{figure}

We are unsure as to the nature of VLA 10. We treat the whole elongated structure as one source. At our higher resolution 4.1 cm image, we can resolve two distinct emission components that are blended at our lower resolution 6.3 cm image (\autoref{fig:serpsouth_vla10_contour}). We cannot confidently rely on our gaussian fitted fluxes or spectral index due to the morphology of the source. For VLA 10's peak flux, we used the Northern structure in the 4.1 cm map. Although our measured peak fluxes are highly uncertain due to confusion at 6.3 cm, VLA 10's peak flux derived spectral index is strongly negative suggesting non-thermal emission and an extragalactic classification. However, VLA 10's Southern structure is also within 2 arcseconds of a Spitzer identified Class I source. This raises the possibility that the Northern structure is a background source while the Southern structure is a Class I protostellar radio source.

Another possibility is that VLA 10 is representative of an outflow shock emanating from either the Southern VLA 10 structure or from sources VLA 11 or 9. An H$_{2}$ study conducted by \citet{Teixeira12}, however, labeled VLA 11 as an outflow source with a jet running from North-East to South-West, almost perpendicular to the direction necessary for it to be an outflow source powering VLA 10's emission. Further evidence that would support a non-extragalactic classification of both the South and North structures of VLA 10 is the fact that the cold dust seen at and longward of 70 $\mu$m neatly fits around VLA 10's elongated morphology, as seen in \autoref{fig:zoom}.

\sourcenote{Protostellar Sources}
The remainder of our 18 sources, VLA 7, 9, 11, 12, 13, 14, 16 and 17 are likely protostellar in nature. With the exception of VLA 9, all of these sources have either flat or rising radio spectral indices indicative of optically thin or thick free-free emission. We classify VLA 12, 13 and 14 as three newly identified embedded Class 0 protostars, separated form each other by less than 15 arcseconds.

@@

@@

\appendix

{\large To Include in Paper:} \\[.1in]

-- Discussion on radio spectral indices and their implications to emission \\

-- Does optically thick radio emission from Spitzer Class I/II source mean anything particularly interesting? B/c it is Spitzer identified, does it mean that it comes not from an ultra-compact region but from some other mechanism? \\
